Meet the team

### 2025-01-27 team.qmd
update images

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Leo Ducharme </h4>
  <p> Undergraduate thesis student </p>
  <p> PNB 4D06 </p>
  </div>
</div>

@@

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Linsea Martin </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

@@

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Dana Rugole </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Biochemistry) </p>
  </div>
</div>

>>>>

<div class="team-member">
  <img src="images/leo-ducharme.jpg" alt="images/leo-ducharme.jpg" class="team-img">
  <div class="team-info">
  <h4> Leo Ducharme </h4>
  <p> Undergraduate thesis student </p>
  <p> PNB 4D06 </p>
  </div>
</div>

@@

<div class="team-member">
  <img src="images/linsea-martin.jpg" alt="images/linsea-martin.jpg" class="team-img">
  <div class="team-info">
  <h4> Linsea Martin </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

@@

<div class="team-member">
  <img src="images/dana-rugole.jpg" alt="images/dana-rugole.jpg" class="team-img">
  <div class="team-info">
  <h4> Dana Rugole </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Biochemistry) </p>
  </div>
</div>
